% !TEX root = tnnls_relation_gait.tex

\ifx\allfiles\undefined
    \input{tnnls_prefix}
\fi

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Depression is a common mental illness that has severe adverse effects on both the individual and society.
Clinical depression is diagnosed by persistent depressive symptoms and assessed by scales, which depend on the general practitioners and cooperative patients.
However, this conventional method is time-consuming and lacks objective metrics.
To address these problems, many auxiliary depression diagnosis studies are explored from different data modalities, making promising progress.
Considering the rapid evolution of this field, this paper aims to provide a comprehensive survey of recent advances in auxiliary depression diagnosis.
Specifically, we introduce two widely used methods in auxiliary depression diagnosis: traditional machine learning and deep learning.
We summarize the general research process and typical research methods while making a performance comparison.
Furthermore, we conclude the survey by highlighting critical applications of auxiliary depression diagnosis and identifying several promising directions for future research.




\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Auxiliary Depression Diagnosis, Machine Learning, Electrophysiological Signals, Brain Imaging, Audiovisual Data, Text
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\ifx\allfiles\undefined
\input{tnnls_suffix}
\fi
